---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(magrittr)
```

## Loading and preprocessing the data
```{r}
activity <- read_csv("activity.zip")
```
Inspect the data set 
```{r}
str(activity)
```

## What is mean total number of steps taken per day?

Calculate the total number of steps per day
```{r}
activity%<>%
  drop_na()%>%
  group_by(date)%>%
  mutate(total_steps=sum(steps))
```

Plot histogramm of total number of steps taken each day  
```{r}
activity%>%
  group_by(date)%>%
  distinct(total_steps, .keep_all=TRUE)%>%
  ggplot()+
  geom_histogram(aes(total_steps), fill="white", color="black")+
  labs(x="total number of steps per day")
```

Calculate the mean and median of the total number of steps taken per day

```{r}
activity%>%
  group_by(date)%>%
  distinct(total_steps, .keep_all=TRUE)%>%
  ungroup%>%
  summarise(mean_steps=mean(total_steps),
            median_steps=median(total_steps))
  
```
**Conclustion**: The median number of steps taken per day was 'r 


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
